Bow shocks, bow waves, and dust waves

### 2017-12-16 papers/Papers1234/sec-dust-bow-intro.tex
Get as far as Rstar in the write-up

>>>>

The internal pressure is the sum of wind ram pressure and the
effective radiation pressure that acts on the bow shell.  The
radiative momentum loss rate of the star is \(L/c\) and the wind
momentum loss rate can be expressed as
\begin{equation}
  \label{eq:wind-efficiency}
  \dot{M} V = \eta L / c \ , 
\end{equation}
where \(\eta\) is the momentum efficiency of the wind, which is typically
\(< 1\) \citep{Lamers:1999b}. If the optical depth is very large, then
all of the stellar radiative momentum, emitted with rate \(L/c\), is
trapped by the bow shell.  In the single scattering
limit,\footnote{Why multiple scattering is not important.} and
temporarily neglecting the wind, then pressure balance at the bow
apex, a distance \(R\) along the symmetry axis from the star is given by
\begin{equation}
  \label{eq:2}
  \frac{L}{4 \pi c R^2} = \rho v^2 \ ,
\end{equation}
which gives a fiducial bow shock radius in this limit as
\begin{equation}
  \label{eq:Rstar}
  R_* = \left(\frac{L}{4\pi c \rho v^2}\right)^{1/2} \ .
\end{equation}
